---
title       : Cars MPG Predictors Presentation
subtitle    : 
author      : Neveen Mohamed
job         : BI and Data Science 2016
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny,bootstrap,interactive,htmlwidgets]       # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

## Presentation Content

This presentation goes over the shiny project delivered in this class. The project uses 
mtcars data and allows an interactive selection of predictors from the dataset to relate with the MPG.


*  Illustration of the input selection to choose the MPG predictors
*  The input is processed at the server to validate selections exist
*  The output chart is displayed

--- .class #id &interactive

## Input parameters
The project uses group select input to allow the user to select the predictor(s) that needs to be researched. 

```{r opts.label='shiny',cache=FALSE,echo=FALSE,error=FALSE,tidy=TRUE, message=FALSE,warning=FALSE,comment=FALSE,prompt=FALSE,results='markup'}

library(slidifyLibraries)
library(shiny)

checkboxGroupInput("params","Parameters",choices=
                       c("disp Displacement (cu.in.)"="disp",
                         "hp   Horse Power"="hp",
                         "drat Rear axle ratio"="drat",
                         "wt   Weight (lb/1000)"="wt",
                         "qsec 1/4 mile time"="qsec",
                         "vs   V/S"="vs",
                         "am   Transmission (0 = automatic, 1 = manual)"="am",
                         "carb Number of carburetors"="carb",
                         "gear Number of forward gears"="gear"))


```

--- .class #id 
## Predictors selection validation

The user clicks on submit button at which point the input parameters get sent to the server,
the server validates the input and displays a message if no selections were made. 


```{r opts.label='shiny',cache=FALSE,echo=FALSE,error=FALSE,tidy=TRUE, message=FALSE,warning=FALSE,comment=FALSE,prompt=FALSE,results='asis'}
   print('Check at least one parameter.')
```

--- .class #id 

## The output chart

If entry is valid the chart gets displayed using googleVis. The chart shows a trend 
exponential fit for the first selected parameter.   
Multiple trend lines are beyond the scope of this project.

```{r opts.label='shiny',cache=FALSE,echo=FALSE,error=FALSE,tidy=TRUE, message=FALSE,warning=FALSE,comment=FALSE,prompt=FALSE,results='asis'}

library(slidifyLibraries)
library(shiny)
library(googleVis)
data(mtcars)

        df <- data.frame(mpg=mtcars$mpg
                         ,disp=mtcars$disp
                         ,hp=mtcars$hp
                         ,drat=mtcars$drat
                         ,wt=mtcars$wt
                         ,qsec=mtcars$qsec
                         ,vs=mtcars$vs
                         ,am=mtcars$am
                         ,carb=mtcars$carb
                         ,gear=mtcars$gear
        )
        G <- 
            gvisScatterChart(
                df, 
                options=list(
                    width=600
                    ,height=400 
                    ,trendlines="{0: { type: 'exponential'}}"))
        
print(G,"chart")

```
