---
title       : Cars MPG Predictors Presentation
subtitle    : 
author      : Neveen Mohamed
job         : BI Analysis and Data Science specialist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny,bootstrap,interactive,htmlwidgets]       # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Presentation Content

This presentation goes over the shiny project delivered in this class. The project uses 
mtcars data and allows an interactive selection of predictors from the dataset to relate with the MPG.

The presentation illustrates the use of interactive R code as follows:
*  ui.R uses check boxs to allow selecting from the indicator list.
*  The input selection is passed in the application to the server.R where is processes it.
*  A message is displayed if no predictors were passed to the server.
*  The output chart is displayed showing the relation between MPG and the predictors.


--- .class #id &interactive

## Selecting the predictors
The project uses a group of check boxes to allow the user to select the predictor(s) that need to be researched. 

Here is what the selections look like:

```{r opts.label='shiny',message=FALSE,error=FALSE,comment=FALSE,prompt= FALSE,echo=FALSE,results='asis'}

data(mtcars)
checkboxGroupInput("params","Parameters",choices=
                         c("disp Displacement (cu.in.)"="disp",
                           "hp   Horse Power"="hp",
                           "drat Rear axle ratio"="drat",
                           "wt   Weight (lb/1000)"="wt",
                           "qsec 1/4 mile time"="qsec",
                           "vs   V/S"="vs",
                           "am   Transmission (0 = automatic, 1 = manual)"="am",
                           "carb Number of carburetors"="carb",
                           "gear Number of forward gears"="gear"))

    
```

--- .class #id 
### Input Validation and Output MPG versus predictors chart


The input from the selectors is sent to server.R which process the selections and displays a chart showing the relation between MPG and the selected predictor(s). googleVis package is used to construct the chart.
If no variables were selected a message is displayed in the output informing the user to make a selection.  

```{r ,cache=FALSE,message=FALSE,error=FALSE,comment=FALSE,warning= FALSE, prompt = FALSE,echo=FALSE,results='asis'}
require(googleVis)
require(shiny)
 
print('Check at least one parameter.')

df <- data.frame(mpg=mtcars$mpg
                 ,disp=mtcars$disp
                 ,hp=mtcars$hp
                 ,drat=mtcars$drat
                 ,wt=mtcars$wt
                 ,qsec=mtcars$qsec
                 ,vs=mtcars$vs
                 ,am=mtcars$am
                 ,carb=mtcars$carb
                 ,gear=mtcars$gear
                 )
G<- gvisScatterChart(
    df, 
    options=list(
        width=600
        ,height=400 
        ,trendlines="{0: { type: 'exponential'}}"))
print(G,"chart")

```





